\begin{thebibliography}{62}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi

\bibitem[{Aboudi(1982)}]{Aboudi1982}
Aboudi, J., \titlecap{A continuum theory for fiber-reinforced
  elastic-viscoplastic composites}, {\em Int. J. Eng.
  Sci.}, vol.~{\bf 20}, no.~5, pp.~605--621, 1982.

\bibitem[{Aboudi(2004)}]{Aboudi2004}
Aboudi, J., \titlecap{The Generalized Method of Cells and High-Fidelity
  Generalized Method of Cells Micromechanical Models{---}A Review},
  {\em Mech. Adv. Mater. Struct.}, vol.~{\bf 11}, nos.~4-5,
  pp.~329--366, 2004.

\bibitem[{Aboudi et~al.(1999)Aboudi, Pindera, and Arnold}]{Aboudi1999}
Aboudi, J., Pindera, M.J., and Arnold, S., \titlecap{Higher-order theory for
  functionally graded materials}, {\em Composites B},
  vol.~{\bf 30}, no.~8, pp.~777--832, 1999.

\bibitem[{Alveen et~al.(2014)Alveen, McNamara, Carolan, Murphy, and
  Ivankovi{\'{c}}}]{Alveen2014}
Alveen, P., McNamara, D., Carolan, D., Murphy, N., and Ivankovi{\'{c}}, A.,
  \titlecap{Analysis of two-phase ceramic composites using micromechanical
  models}, {\em Comput. Mater. Sci.}, vol.~{\bf 92}, pp.~318--324,
  2014.

\bibitem[{Alveen et~al.(2015)Alveen, McNamara, Carolan, Murphy, and
  Ivankovi{\'{c}}}]{Alveen2015}
Alveen, P., McNamara, D., Carolan, D., Murphy, N., and Ivankovi{\'{c}}, A.,
  \titlecap{The influence of microstructure on the fracture properties of
  polycrystalline cubic boron nitride}, {\em Comput. Mater. Sci.},
  vol.~{\bf 109}, pp.~115--123, 2015.

\bibitem[{Avery et~al.(2021)Avery, Huang, He, Ehlers, Derkevorkian, and
  Farhat}]{Avery2021}
Avery, P., Huang, D.Z., He, W., Ehlers, J., Derkevorkian, A., and Farhat, C.,
  \titlecap{A computationally tractable framework for nonlinear dynamic
  multiscale modeling of membrane woven fabrics}, {\em Int. J.
    Numer. Methods Eng.}, vol.~{\bf 122}, no.~10,
  pp.~2598--2625, 2021.

\bibitem[{Badia et~al.(2007)Badia, Bochev, Lehoucq, Parks, Fish, Nuggehally,
  and Gunzburger}]{Badia2007}
Badia, S., Bochev, P., Lehoucq, R., Parks, M.L., Fish, J., Nuggehally, M.A.,
  and Gunzburger, M., {A Force-Based Blending Model
  for Atomistic-to-Continuum Coupling}, {\em Int. J.
  Multiscale Comput. Eng.}, vol.~{\bf 5}, no.~5, pp.~387--406,
  2007.

\bibitem[{Belytschko and Black(1999)}]{Belytschko1999}
Belytschko, T. and Black, T., \titlecap{Elastic crack growth in finite elements
  with minimal remeshing}, {\em Int. J. Numer. Methods
  Eng.}, vol.~{\bf 45}, no.~5, pp.~601--620, 1999.

\bibitem[{Berlyand and Kolpakov(2001)}]{Berlyand2001}
Berlyand, L. and Kolpakov, A., \titlecap{Network Approximation in the Limit
  of Small Interparticle Distance of
  the Effective Properties of a
  High-Contrast Random Dispersed Composite}, {\em Arch.
  Ration. Mech. Anal.}, vol.~{\bf 159}, no.~3, pp.~179--227, 2001.

\bibitem[{Bhattacharjee and Matou{\v{s}}(2016)}]{Bhattacharjee2016}
Bhattacharjee, S. and Matou{\v{s}}, K., \titlecap{A nonlinear manifold-based
  reduced order model for multiscale analysis of heterogeneous hyperelastic
  materials}, {\em J. Comput. Phys.}, vol.~{\bf 313},
  pp.~635--653, 2016.

\bibitem[{Cardiff and Demird{\v{z}}i{\'{c}}(2021)}]{Cardiff2021}
Cardiff, P. and Demird{\v{z}}i{\'{c}}, I., \titlecap{Thirty Years of the Finite
  Volume Method for Solid Mechanics}, {\em Arch. Comput. Methods
  Eng.}, vol.~{\bf 28}, no.~5, pp.~3721--3780, 2021.

\bibitem[{Cardiff et~al.(2016)Cardiff, Tukovi{\'{c}}, Jaeger, Clancy, and
  Ivankovi{\'{c}}}]{Cardiff2016}
Cardiff, P., Tukovi{\'{c}}, {\v{Z}}., Jaeger, P.D., Clancy, M., and
  Ivankovi{\'{c}}, A., \titlecap{A Lagrangian cell-centred finite volume method
  for metal forming simulation}, {\em Int. J. Numer.
  Methods   Eng.}, vol.~{\bf 109}, no.~13, pp.~1777--1803, 2016.

\bibitem[{Carolan et~al.(2015)Carolan, Chong, Ivankovic, Kinloch, and
  Taylor}]{Carolan2015}
Carolan, D., Chong, H., Ivankovic, A., Kinloch, A., and Taylor, A.,
  \titlecap{Co-continuous polymer systems: A
nume
ultiscale Modeling: A Review}, in {\em Practical Aspects
  of Computational Chemistry}, Netherlands: Springer, pp.~87--135, 2009.

\bibitem[{Jasak and Weller(2000)}]{Jasak2000}
Jasak, H. and Weller, H.G., \titlecap{Application of the finite volume method
  and unstructured meshes to linear elasticity}, {\em Int. J.
  Numer. Methods   Eng.} vol.~{\bf 48}, no.~2,
  pp.~267--287, 2000.

\bibitem[{Kanout{\'{e}} et~al.(2009)Kanout{\'{e}}, Boso, Chaboche, and
  Schrefler}]{Kanout2009}
Kanout{\'{e}}, P., Boso, D.P., Chaboche, J.L., and Schrefler, B.A.,
  \titlecap{Multiscale Methods for Composites: A Review}, {\em Arch.
  Comput. Methods   Eng.}, vol.~{\bf 16}, no.~1, pp.~31--75,
  2009.

\bibitem[{Karabasov et~al.(2014)Karabasov, Nerukh, Hoekstra, Chopard, and
  Coveney}]{Karabasov2014}
Karabasov, S., Nerukh, D., Hoekstra, A., Chopard, B., and Coveney, P.V.,
  \titlecap{Multiscale modelling: Approaches and challenges}, {\em
  Philos. Trans. R. Soc. A}, vol.~{\bf 372}, no.~2021, p.~20130390, 2014.

\bibitem[{Kouznetsova et~al.(2002)Kouznetsova, Geers, and
  Brekelmans}]{Kouznetsova2002}
Kouznetsova, V., Geers, M.G.D., and Brekelmans, W.A.M., \titlecap{Multi-scale
  constitutive modelling of heterogeneous materials with a gradient-enhanced
  computational homogenization scheme}, {\em Int. J.
  Numer. Methods   Eng.}, vol.~{\bf 54}, no.~8, pp.~1235--1260,
  2002.

\bibitem[{Krysl et~al.(2001)Krysl, Lall, and Marsden}]{Krysl2001}
Krysl, P., Lall, S., and Marsden, J.E., \titlecap{Dimensional model reduction
  in non-linear finite element dynamics of solids and structures}, {\em
  Int. J. Numer. Methods   Eng.}, vol.~{\bf 51},
  no.~4, pp.~479--504, 2001.

\bibitem[{Le et~al.(2015)Le, Yvonnet, and He}]{Le2015}
Le, B.A., Yvonnet, J., and He, Q.C., \titlecap{Computational homogenization of
  nonlinear elastic materials using neural networks}, {\em Int.
  J. Numer. Methods   Eng.}, vol.~{\bf 104}, no.~12,
  pp.~1061--1084, 2015.

\bibitem[{Lee et~al.(2017)Lee, Li, Zhang, and Wang}]{Lee2017}
Lee, J.D., Li, J., Zhang, Z., and Wang, L., \titlecap{Sequential and concurrent
  multiscale modeling of multiphysics: From atoms to continuum}, {\em
  Micromechanics and Nanomechanics of Composite Solids}, Cham, Switzerland: Springer, pp.~1--38, 2017.

\bibitem[{Leonard et~al.(2012)Leonard, Murphy, Kara{\v{c}}, and
  Ivankovi{\'{c}}}]{Leonard2012}
Leonard, M., Murphy, N., Kara{\v{c}}, A., and Ivankovi{\'{c}}, A., \titlecap{A
  numerical investigation of spherical void growth in an
  elastic{\textendash}Plastic continuum}, {\em Comput. Mater.
  Sci.}, vol.~{\bf 64}, pp.~38--40, 2012.

\bibitem[{Markl and Korner(2016)}]{annurev-matsci}
Markl, M. and K\"{o}rner, C., \titlecap{Multiscale Modeling of Powder Bed-Based
  Additive Manufacturing}, {\em Ann. Rev. Mater. Res.}, vol.~{\bf
  46}, no.~1, pp.~93--123, 2016.

\bibitem[{Matou{\v{s}} et~al.(2017)Matou{\v{s}}, Geers, Kouznetsova, and
  Gillman}]{Matou2017}
Matou{\v{s}}, K., Geers, M.G., Kouznetsova, V.G., and Gillman, A., \titlecap{A
  review of predictive nonlinear theories for multiscale modeling of
  heterogeneous materials}, {\em J. Comput. Phys.}, vol.~{\bf
  330}, pp.~192--220, 2017.

\bibitem[{McNamara et~al.(2014)McNamara, Alveen, Carolan, Murphy, and
  Ivankovi{\'{c}}}]{McNamara2014}
McNamara, D., Alveen, P., Carolan, D., Murphy, N., and Ivankovi{\'{c}}, A.,
  \titlecap{Micromechanical Study of Strength and Toughness of Advanced
  Ceramics}, {\em Procedia Mater. Sci.}, vol.~{\bf 3}, pp.~1810--1815,
  2014.

\bibitem[{McNamara et~al.(2015)McNamara, Alveen, Damm, Carolan, Rice, Murphy,
  and Ivankovi{\'{c}}}]{McNamara2015}
McNamara, D., Alveen, P., Damm, S., Carolan, D., Rice, J.H., Murphy, N., and
  Ivankovi{\'{c}}, A., \titlecap{A Raman spectroscopy investigation into the
  influence of thermal treatments on the residual stress of polycrystalline
  diamond}, {\em Int. J. Refract. Metals   Hard
  Mater.}, vol.~{\bf 52}, pp.~114--122, 2015.

\bibitem[{Michel and Suquet(2004)}]{Michel2004}
Michel, J. and Suquet, P., \titlecap{Computational analysis of nonlinear
  composite structures using the

ara{\v{c}}, Cardiff, Jasak,
  and Ivankovi{\'{c}}}]{Tukovic2018}
Tukovi{\'{c}}, {\v{Z}}., Kara{\v{c}}, A., Cardiff, P., Jasak, H., and
  Ivankovi{\'{c}}, A., \titlecap{{OpenFOAM} Finite Volume Solver for
  Fluid-Solid Interaction}, {\em Trans. {FAMENA}}, vol.~{\bf 42},
  no.~3, pp.~1--31, 2018.

\bibitem[{Tukovi\'{c} et~al.(2019)Tukovi\'{c}, Wu, Cardiff, and
  Ivankovi{\'{c}}}]{Tukovic2019}
Tukovi\'{c}, {\v{Z}}., Wu, K., Cardiff, P., and Ivankovi{\'{c}}, A.,
  \titlecap{Finite volume multiscale modelling of solid mechanics problems},
  in {\em 4th Int. Conf. on Multi-scale Computational Methods for
  Solids and Fluids}, A. Ivankovi{\'{c}} and K. Hanjali\'{c}, Eds.,   University of Sarajevo, Sarajevo, Bosnia and Herzegovina, 2019.

\bibitem[{Wagner and Liu(2003)}]{Wagner2003}
Wagner, G.J. and Liu, W.K., \titlecap{Coupling of atomistic and continuum
  simulations using a bridging scale decomposition}, {\em J.
  Comput. Phys.}, vol.~{\bf 190}, no.~1, pp.~249--274, 2003.

\bibitem[{Weller et~al.(1998)Weller, Tabor, Jasak, and Fureby}]{Weller1998}
Weller, H.G., Tabor, G., Jasak, H., and Fureby, C., \titlecap{A tensorial
  approach to computational continuum mechanics using object-oriented
  techniques}, {\em Comput. Phys.}, vol.~{\bf 12}, no.~6, p.~620, 1998.

\bibitem[{Xiao and Belytschko(2004)}]{Xiao2004}
Xiao, S. and Belytschko, T., \titlecap{A bridging domain method for coupling
  continua with molecular dynamics}, {\em Comput. Methods   Appl. Mech.
    Eng.}, vol.~{\bf 193}, nos.~17-20, pp.~1645--1669, 2004.

\bibitem[{Yashchuk(2018)}]{Yashchuk2018}
Yashchuk, I., \titlecap{A multiscale finite element framework for
  additive manufacturing process modeling}, MS, Aalto University,
  School of Engineering, Espoo, Finland, 2018.

\bibitem[{Yvonnet and He(2007)}]{Yvonnet2007}
Yvonnet, J. and He, Q.C., \titlecap{The reduced model multiscale method (R3M)
  for the non-linear homogenization of hyperelastic media at finite strains},
  {\em J. Comput. Phys.}, vol.~{\bf 223}, no.~1, pp.~341--368,
  2007.

\bibitem[{Zeng and Qin(2018)}]{ZENG2018269}
Zeng, Q. and Qin, Y., Multiscale Modeling of Hybrid Machining Processes, in \textit{Hybrid Machining}, X. Luo and Y. Qin, Eds., New York: Academic Press, pp. 269--298, 2018.

\bibitem[{Allaire, 2002}]{Allaire2002}
Allaire, G., {\em Shape optimization by the homogenization method},
 New York: Springer, 2002.

\end{thebibliography}
